---
title: "clean_excerpts"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In Progress

## Purpose

Preliminary cleaning script for the full survey data, constructed using excerpt files provided by Adam previously. The primary intent is to make a script that is easily adaptable for cleaning the full dataset once provided.

## Setup

```{r}
library(tidyverse)

# Point to data folders in the repo
path_org <- 'data_org'
path_clean <- 'data_clean'

# Load in excerpt files
prca <- read_csv(here::here(path_org, 'prca_excerpt.csv'))
demos <- read_csv(here::here(path_org, 'demo_excerpt.csv'))
  
# Join together — prca is the primary table; demos adds Prolific demographic columns
survey <- full_join(prca, demos, by = c("PROLIFIC_PID" = "Participant id"))
```

Preliminary EDA reveals two anomalous entries in certain fields. CONSENT_REVOKED and DATA_EXPIRED
*Load in excerpt files*

```{r}
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
